Interpretable Machine Learning for Science \\ with PySR and SymbolicRegression.jl

### 2023-08-03 src/tex/ms.tex
Remove extra heading info
Remove date
Add line numbers
Fix quotation

@@

\usepackage{cleveref} \begin{document}
\newcommand\myhref[2]{\textsf{\textcolor{blue}{\href{#1}{#2}}}}
\newcommand\giturl{\myhref{https://github.com/MilesCranmer/pysr_paper}{github.com/MilesCranmer/pysr\_paper}}

\titlehead{
    \begin{center}
    \parbox{0.3\textwidth}{
        \hfill
        \emph{PySR \& SymbolicRegression.jl}
    }
    \hspace{2in}
    \parbox{0.3\textwidth}{
        \giturl
        \hfill
    }
    \end{center}
}

\title{Interpretable Machine Learning for Science \\ with PySR and SymbolicRegression.jl}
\author[1,2]{Miles Cranmer}
\affil[1]{Princeton University, Princeton, NJ, USA}
\affil[2]{Flatiron Institute, New York, NY, USA}
\date{May 2, 2023}

\twocolumn[\begin{@twocolumnfalse}
\maketitle
\begin{abstract}
\addtocounter{footnote}{2}
\pysr\footnotemark{} is an open-source library for practical \textit{symbolic regression}, a type of machine learning which aims to discover human-interpretable symbolic models.
\pysr was developed to democratize and popularize symbolic regression for the sciences, and is built on a high-performance distributed backend, a flexible search algorithm, and interfaces with several deep learning packages.
\pysr's internal search algorithm is a multi-population evolutionary algorithm, which consists of a unique evolve-simplify-optimize loop, designed for optimization of unknown scalar constants in newly-discovered empirical expressions.
\pysr's backend is an extremely optimized Julia library \pysrjlabs\footnotemark{},
which can be used directly from Julia. It is capable of fusing user-defined operators into SIMD kernels at runtime, performing automatic differentiation, and distributing populations of expressions to thousands of cores across a cluster.
In describing this software, we also introduce a new benchmark, ``\textit{EmpiricalBench},’’ to quantify the applicability of symbolic regression algorithms in science.
This benchmark measures recovery of historical empirical equations from original and synthetic datasets.
\end{abstract}
\end{@twocolumnfalse}
]

@@

@@

This brings us to an optimization problem known ``symbolic regression,'' or SR.
In this paper, we describe an algorithm for performing SR, and describe software dedicated to equation discovery in the sciences.

@@

Miles Cranmer would like to thank
the Simons Foundation for providing resources for pursuing this research;
Shirley Ho and David Spergel for countless insightful discussions about \pysr, feedback on this manuscript, promotion of it as a tool in the sciences, and for their support of this project;
my research collaborators who provided feedback throughout the development of \pysr, including Pablo Lemos, Peter Battaglia, Steve Brunton, Jay Wadekar, Paco Villaescusa-Navarro, Kaze Wong, Elaine Cui, Christina Kreisch, Nathan Kutz, Drummond Fielding, Keaton Burns, Dima Kochkov, Alvaro Sanchez-Gonzalez, Christian Jespersen, Patrick Kidger, Kyle Cranmer, Niall Jeffrey, Ana Maria Delgado, Keming Zhang, Pierre-Alexandre Kamienny, Michael Douglas, Francois Charton;
all the wonderful open-source code contributors, including Mark Kittisopikul, T Coxon, Dhananjay Ashok, Johan Blåbäck, Julius Martensen, GitHub user \texttt{@ngam}, Christopher Rackauckas, Jerry Ling, Charles Fox, Johann Brehmer, Marius Millea, GitHub user \texttt{@Coba}, Pietro Monticone, Mateusz Kubica, GitHub user \texttt{@Jgmedina95}, Michael Abbott, Oscar Smith, and several others;
Marco Virgolin for extremely helpful comments on a draft of this paper, as well as general feedback;
Bill La Cava for providing feedback as well as spearheading the SRBench initiative, along with the rest of the SRBench organizers;
Brenden Petersen for feedback on \pysr as well as providing insights discussions about the SR landscape;
and so many others who have provided support to the project through email, Twitter, GitHub issues, and in-person.
I am blown away by the community that is forming around \pysr and the positive feedback it has received. Thank you.

>>>>

\usepackage[switch]{lineno}

@@

\usepackage{cleveref}
\begin{document}

\newcommand\myhref[2]{\textsf{\textcolor{blue}{\href{#1}{#2}}}}
\newcommand\giturl{\myhref{https://github.com/MilesCranmer/pysr_paper}{github.com/MilesCranmer/pysr\_paper}}

\titlehead{
    \begin{center}
    \parbox{0.3\textwidth}{
        \hfill
        \emph{PySR \& SymbolicRegression.jl}
    }
    \hspace{2in}
    \parbox{0.3\textwidth}{
        \hphantom{\giturl}
        \hfill
    }
    \end{center}
}

\title{Interpretable Machine Learning for Science \\ with PySR and SymbolicRegression.jl}
\author[1,2]{Miles Cranmer}
\affil[1]{Princeton University, Princeton, NJ, USA}
\affil[2]{Flatiron Institute, New York, NY, USA}
\date{}

\twocolumn[\begin{@twocolumnfalse}
\maketitle
\begin{abstract}
\addtocounter{footnote}{2}
\pysr\footnotemark{} is an open-source library for practical \textit{symbolic regression}, a type of machine learning which aims to discover human-interpretable symbolic models.
\pysr was developed to democratize and popularize symbolic regression for the sciences, and is built on a high-performance distributed backend, a flexible search algorithm, and interfaces with several deep learning packages.
\pysr's internal search algorithm is a multi-population evolutionary algorithm, which consists of a unique evolve-simplify-optimize loop, designed for optimization of unknown scalar constants in newly-discovered empirical expressions.
\pysr's backend is an extremely optimized Julia library \pysrjlabs\footnotemark{},
which can be used directly from Julia. It is capable of fusing user-defined operators into SIMD kernels at runtime, performing automatic differentiation, and distributing populations of expressions to thousands of cores across a cluster.
In describing this software, we also introduce a new benchmark, ``\textit{EmpiricalBench},'' to quantify the applicability of symbolic regression algorithms in science.
This benchmark measures recovery of historical empirical equations from original and synthetic datasets.
\end{abstract}
\end{@twocolumnfalse}
]

@@

\begin{linenumbers}

@@

This brings us to an optimization problem known as ``symbolic regression,'' or SR.
In this paper, we describe an algorithm for performing SR, and describe software dedicated to equation discovery in the sciences.

@@

Miles Cranmer would like to thank
the Simons Foundation for providing resources for pursuing this research;
Shirley Ho and David Spergel for countless insightful discussions about \pysr, feedback on this manuscript, promotion of it as a tool in the sciences, and for their support of this project;
my research collaborators who provided feedback throughout the development of \pysr, including Pablo Lemos, Peter Battaglia, Steve Brunton, Jay Wadekar, Paco Villaescusa-Navarro, Kaze Wong, Elaine Cui, Christina Kreisch, Nathan Kutz, Drummond Fielding, Keaton Burns, Dima Kochkov, Alvaro Sanchez-Gonzalez, Christian Jespersen, Patrick Kidger, Kyle Cranmer, Niall Jeffrey, Ana Maria Delgado, Keming Zhang, Pierre-Alexandre Kamienny, Michael Douglas, Francois Charton;
all the wonderful open-source code contributors, including Mark Kittisopikul, T Coxon, Dhananjay Ashok, Johan Blåbäck, Julius Martensen, GitHub user \texttt{@ngam}, Christopher Rackauckas, Jerry Ling, Charles Fox, Johann Brehmer, Marius Millea, GitHub user \texttt{@Coba}, Pietro Monticone, Mateusz Kubica, GitHub user \texttt{@Jgmedina95}, Michael Abbott, Oscar Smith, and several others;
Marco Virgolin for extremely helpful comments on a draft of this paper, as well as general feedback;
Bill La Cava for providing feedback as well as spearheading the SRBench initiative, along with the rest of the SRBench organizers;
Brenden Petersen for feedback on \pysr as well as providing insights discussions about the SR landscape;
and so many others who have provided support to the project through email, Twitter, GitHub issues, and in-person.
% I am blown away by the community that is forming around \pysr and the positive feedback it has received. Thank you.

\end{linenumbers}
